Make any stupid plot you want

### 2020-11-30 draft/sections/math.tex
pictures & not so many words
rewrote intro to math section w/ more context

\section{Notation \& Definitions}
%%% add some words around

\begin{equation}
    A: \Gamma(E) \rightarrow \Gamma(H)
\end{equation}

%% E is a locally trivial fiber bundle over K where K is triangulizable space representing data space & H is a fiber bundle over S which is a simplacial complex of triangles representing visual space and artists in matplotlib will go between the two. E is a trivial fiber bundle $E = F \times K$, it can be assumed that all $F_{k}$ for $k \in K$ are equal.

%% locally trival bundle is map from one topoligical space E to another K such that around any point in K there exists an open set containing that point such that if we restrict E to that part, it's quivalent to (homoemorphic to) open set cross fiber. 
%%  
\subsection{Data Model}
\begin{figure}[ht]
    \caption{write up some words here}
    \label{fig:fiberbundle}
    %%possibly replace w/ simpler deconstructed band image notes-11-19-20
    %% or replace w/ box w/ thing that's kind of convoluted 
    %% simpler still replace w/ timeseries of temp, 1D fiber -> inspired by butler 1989 FIgG 1
\end{figure}

@@

One example of a fiber bundle is shown in figure~\ref{fig:mobius}. A fiber bundle is a topological total space $E$ with an embedded fiber space $F$, a base space on which the fibers lie $K$ and the $\pi$ and $\sigma$ mappings between $E$ and $K$.

@@

\subsubsection{Base Space $K$}

%% general statement about topology, examples of 0, 1, ....Ks [none triangular things, square/torus, ....], condition on K is that it can be represent as a triangulation of K (can be realized as triangle on K - extra structure that may be arbitrary
%% k is a topological space ....equation soup

\subsubsection{Fiber Space $F$}
\begin{figure}
    \includegraphics{}
    \label{fig:movie}
\end{figure}
%%% might 
The fibers encode the set of all possible values each observation can take. For example, the fiber in figure~\ref{fig:temp} is the space of possible temperature values in $\circ$ celsius, ranging from [start, end]. In figure~\ref{fig:temp_time}, time is encoded as a second dimension and since the data is from 2019 the value t

>>>>

\section{Notation \& Definitions}
In this section we introduce a mathematical formulation of the visualization pipeline where artist $A$ functions transform data $\Gamma(E)$ to an intermediate representation in prerendered display space $Gamme(H)$:

\begin{equation}
    A: \Gamma(E) \rightarrow \Gamma(H)
    \lab{eq:artist}
\end{equation}

$E$ is a locally trivial fiber bundle over $K$ representing data space; $K$ is a triangulizable space encoding the connectivity of the observations in the data. $H$ is a fiber bundle over $S$ representing visual space;  $S$ is a simplacial complex of triangles encoding the connectivity of the visual output of each artist $A$. When E is a trivial fiber bundle $E = F \times K$, it can be assumed that all $F_{k}$ for $k \in K$ are equal.

\begi

\subsection{Data Model}
\begin{figure}[ht]
    \label{fig:fiberbundle}
    \includegraphics{figures/sections/math/fiberbundle.png}
    \caption{write up some words here}

    %% simpler still replace w/ timeseries of temp, 1D fiber -> inspired by butler 1989 FIgG 1
\end{figure}

@@

A fiber bundle is a topological total space $E$ with an embedded fiber space $F$, a base space on which the fibers lie $K$ and the $\pi$ and $\sigma$ mappings between $E$ and $K$.

@@

\subsubsection{Base Space $K$}
\begin{figure}
    \includegraphics{figures/sections/math/temp_1k.png}
\end{figure}
\begin{figure}
    \includegraphics{figures/sections/math/temp_2k.png}
\end{figure}
%% general statement about topology, examples of 0, 1, ....Ks [none triangular things, square/torus, ....], condition on K is that it can be represent as a triangulation of K (can be realized as triangle on K - extra structure that may be arbitrary
%% k is a topological space ....equation soup

\subsubsection{Fiber Space $F$}
\begin{figure}
    \includegraphics{figures/sections/math/temp_2f.png}
    \label{fig:}
\end{figure}
\begin{figure}
    \includegraphics{figures/sections/math/temp_3f.png}
\end{figures}
%%% might 
The fibers encode the set of all possible values each observation can take. For example, the fiber in figure~\ref{fig:temp} is the space of possible temperature values in $\circ$ celsius, ranging from [start, end]. In figure~\ref{fig:temp_time}, time is encoded as a second dimension and since the data is from 2019 the value t
